Catchy Title Goes Here

### 2018-05-03 Paper/paper.tex
more figures, more chains
small updates, notes on citations added

\section{Introduction \label{sec:Intro}}
- Quantifying the size and age distribution of the population susceptible to measles is a critical tool in evaluating vaccination programs and developing interventions.  
- Unfortunately, direct observation of the susceptible population is challenging as it requires a sero-survey which can be cost-prohibitive.
- Previous efforts have estimated the susceptible distribution though demographic models that account for inputs through births and immunization via both vaccination an natural infection.
	- Winter et al (new paper on Madagascar)
	- Merler and the Italian group (http://www.thelancet.com/pdfs/journals/laninf/PIIS1473-3099(17)30421-8.pdf)
- The contribution of natural infection to population immunity can be challenging to estimate. In particular, the age-specific force of infection is not directly estimable from aggregate population time series ? (both papers referenced above rely on SIR models that assume a specific age-structured mixing)

@@

Further, vaccination does not necessarily imply immunization.  The efficacy of measles vaccine is often assumed to be ... (see Uzicanin article) though is also known to improve with age as older children are more likely to have lost maternally transferred antibodies (se many). The effectiveness of vaccine delivered in field settings may also vary dramatically due to stability and effectiveness of the vaccine cold chain.  A comparison of the age-distribution of vaccination and sero-prevalence may highlight areas with low effectiveness, and absent a sero-survey this assessment could be made using age-specific case records.

@@

The functional forms of $f(a)$ and $v(a)$ are free to be specified. In this study, we choose to use un-normalized Weibull distributions to parameterize both of these functions, as they have been shown to be sufficiently flexible to match a range of possible forces of infection and vaccination hazards. Thus $f(a) \rightarrow f(a|\mathbb{\psi})$ and $v(a) \rightarrow v(a|\mathbb{\theta})$, where $\mathbb{\psi}$ and $\mathbb{\theta}$ are vectors of the parameters we use for the Weibull distribution - height ($\eta$), scale ($\alpha$), and shape ($\beta$). This gives six parameters that fully specify the forms of $f(a)$ and $v(a)$ from Eq.~\ref{eq:CatModSum} - $\alpha$, $\beta$, and $\eta$ for two independent Weibull distributions. To allow for the fact that not all vaccinations produce immunity, we introduce a seventh parameter - the vaccine effectiveness ($\gamma$). This enters the equation as a multiplier on $v(a)$ that ranges between $0.0$ and $1.0$.

@@

The data we work with (described in detail in Sec.~\ref{subsec:Data}) consists of cases as a function of age, serology tests and results as a function of age, and vaccination status as a function of age for a sample of individuals within a particular province. The likelihood for observing this dataset given values for the model parameters as
\begin{align}
\log \mathcal{L} (\mathbf{c}, \mathbf{v_t}, \mathbf{v_o}, \mathbf{s_t},&\mathbf{s_o}|\eta_f, \alpha_f, \beta_f, \gamma, \eta_v, \alpha_v, \beta_v)\nonumber \\ 
& = \sum_aB\left(v_o(a), v_t(a); p(\mathrm{vaccinated}|a)\right) \nonumber \\
&+ \sum_a B\left(s_o(a),s_t(a);p(\mathrm{immune}|a)\right) \nonumber \\
&+ M\left(\mathbf{c};p(\mathrm{case}|a)\right),
\label{eq:loglike}
\end{align}
where $s_t$ is the total number of individuals tested for IgM seropositivity, and $s_o$ is the number of positive tests; and $v_t$ is the number of individuals surveyed about vaccination status, while $v_o$ gives the number who have been vaccinated. $B$ represents a binomial probability, and $M$ represents a multinomial distribution, and the sums are over age classes. As noted, each data point includes the age of the individual in question.

@@

\subsection{DRC Data \label{subsec:DRC}}
Application to the DRC data
	Pairs plots for all provinces ? compare for fits with only case data to fits with case+serology ? discuss any appearance of non-identifiability 	
Figure 2 ? pairs plots for all provinces and two models

>>>>

\section{Introduction \label{sec:Intro}}
- Quantifying the size and age distribution of the population susceptible to measles is a critical tool in evaluating vaccination programs and developing interventions (Winter et al JID; Cutts and Hanson TMIH).  
- Unfortunately, direct observation of the susceptible population is challenging as it requires a sero-survey which can be cost-prohibitive (Winter et al JID paper). 
- Previous efforts have estimated the susceptible distribution though demographic models that account for inputs through births and immunization via both vaccination an natural infection.
	- Winter et al (new paper on Madagascar)
	- Merler and the Italian group (http://www.thelancet.com/pdfs/journals/laninf/PIIS1473-3099(17)30421-8.pdf)
- The contribution of natural infection to population immunity can be challenging to estimate. In particular, the age-specific force of infection is not directly estimable from aggregate population time series ? (both papers referenced above rely on SIR models that assume a specific age-structured mixing). 
	- challenges of using historical incidence data -- under-reporting, changing reporting.

@@

Further, vaccination does not necessarily imply immunization.  The efficacy of measles vaccine is often assumed to be ... (see Uzicanin article) though is also known to improve with age as older children are more likely to have lost maternally transferred antibodies (se many). The effectiveness of vaccine delivered in field settings may also vary dramatically due to stability and effectiveness of the vaccine cold chain (Doshi et al 2017 Vaccine).  A comparison of the age-distribution of vaccination and sero-prevalence may highlight areas with low effectiveness, and absent a sero-survey this assessment could be made using age-specific case records.

Routine vaccination coverage surveys and age-specific case reporting are more readily available data sources (see Takahashi text re: DHS).

@@

The functional forms of $f(a)$ and $v(a)$ are free to be specified. In this study, we choose to use un-normalized Weibull distributions to parameterize both of these functions, as they have been shown to be sufficiently flexible to match a range of possible forces of infection and vaccination hazards[REF]. Thus $f(a) \rightarrow f(a|\mathbb{\psi})$ and $v(a) \rightarrow v(a|\mathbb{\theta})$, where $\mathbb{\psi}$ and $\mathbb{\theta}$ are vectors of the parameters we use for the Weibull distribution - height ($\eta$), scale ($\alpha$), and shape ($\beta$). This gives six parameters that fully specify the forms of $f(a)$ and $v(a)$ from Eq.~\ref{eq:CatModSum} - $\alpha$, $\beta$, and $\eta$ for two independent Weibull distributions. To allow for the fact that not all vaccinations produce immunity, we introduce a seventh parameter - the vaccine effectiveness ($\gamma$). This enters the equation as a multiplier on $v(a)$ that ranges between $0.0$ and $1.0$.

@@

The data we work with (described in detail in Sec.~\ref{subsec:Data}) consists of the number cases as a function of age (in years), serology tests and results as a function of age, and vaccination status as a function of age for a sample of individuals within a particular province. The likelihood for observing this dataset given values for the model parameters as
\begin{align}
\log \mathcal{L} (\mathbf{c}, \mathbf{v_t}, \mathbf{v_o}, \mathbf{s_t},&\mathbf{s_o}|\eta_f, \alpha_f, \beta_f, \gamma, \eta_v, \alpha_v, \beta_v)\nonumber \\ 
& = \sum_aB\left(v_o(a), v_t(a); p(\mathrm{vaccinated}|a)\right) \nonumber \\
&+ \sum_a B\left(s_o(a),s_t(a);p(\mathrm{immune}|a)\right) \nonumber \\
&+ M\left(\mathbf{c};p(\mathrm{case}|a)\right),
\label{eq:loglike}
\end{align}
where $s_t$ is the total number of individuals tested for IgM seropositivity, and $s_o$ is the number of positive tests; and $v_t$ is the number of individuals surveyed about vaccination status, while $v_o$ gives the number who have been vaccinated. $B$ represents a binomial probability, and $M$ represents a multinomial distribution, and the sums are over age classes. As noted, each data point includes the age of the individual in question.

@@

\subsection{DRC Data \label{subsec:DRC}}
Application to the DRC data
	Pairs plots for all provinces ? compare for fits with only case data to fits with case+serology ? discuss any appearance of non-identifiability (?? What is non-identifiability?)	
Figure 2 ? pairs plots for all provinces and two models
